Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Edit Appendix A

    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
    objects around the target.
    At the depth of the HSC images, this becomes a challenging task, especially 
    for massive galaxies with extended outer profiles and many satellites. 
    Right now, the \texttt{hscPipe} tends to ``over-deblend'' around bright object, 
    we therefore perform \texttt{SExtractor}-like background subtraction and object 
    detection using the \texttt{SEP} Python library to generate the necessary masks.
    Combining two different local background models and $S/N$ thresholds, we obtain 
    the centroid, shape, and radius that enclose 90\% of flux for each object, even 
    the one that is close to the center of bright galaxy (left panel of 
    Fig~\ref{fig:ell_tech}), and generate its initial elliptical mask based on these
    information. 
    We first create the mask that covers all contaminating objects around the target 
    after adaptively increasing the sizes of their masks according to their brightness 
    and distance to the target center. 
    Generally speaking, we mask out the very bright objects or objects in the 
    outskirt of the target a little more aggressively as they could impact the 
    low surface brightness regions more significantly. 
    We also create masks that are less and more aggressive to test their impacts
    on the surface brightness profiles.

    Next, we aggressively mask out all objects on the cut-out image and use this mask
    to evaluate the background level using the distribution of pixel values after 
    median smoothing the masked image within $6x6$ pixels.
    This provides us a global estimate of background level along with its uncertainty. 
    Given the typical RMS of the background pixels, the HSC \texttt{WIDE} images 
    should reach to $> 29$ \sb surface brightness level in $i$-band.  
    However, the global background level is often negative around our massive 
    galaxies, indicating systematic issue in background subtraction.  
    In current \texttt{hscPipe}, the background on each CCD is modeled with a 
    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
    with $S/N >5$.
    This algorithm performs much better than the SDSS version 
    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts sky around bright 
    objects and results in unphysical truncation in the surface brightness profile.
    We attempt to empirically correct this using the background model generated by 
    the \texttt{SExtractor} algorithm on the masked image 
    ($200x200$ pixels background box size, and 6 pixels median filtering size of 
    sky boxes).
    This model can account for the slightly over-subtracted background at large scale,
    and also reduces the impact from the low surface brightness ``wings'' of bright 
    nearby objects. 
    After the correction, we can see the improvement from both the remeasured global 
    background value (closer to 0) and the surface brightness profile (middle panel 
    of Fig~\ref{app:ellipse}; the negative intensity and the turn-over of the 
    curve-of-growth in the outskirt of the ``Original'' profile are successfully 
    corrected). 
    Such ad hoc correction is not the best way to achieve accurate background 
    subtraction, but the surface brightness profile within 100 kpc is not very
    sensitive to the over-subtraction of sky as while.

    The procedure to derive 1-D surface brightness profile from the 
    background-corrected, contamination-masked images is already described in 
    Section~\ref{sec:ellipse} briefly. 
    In practice, the profile at very low surface brightness level is sensitive to 
    several \texttt{Ellipse} configurations.
    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    axis length between successive ellipses, and we use the median pixel value over the
    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
    times.
    We make the above choices to make the final profile less affected by any nearby
    object, and also test the differences between the profiles derived using larger
    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
    Generally speaking, the surface brightness profile is very robust against these
    changes.  
    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
    parameters. 
    The profile within 100 kpc is very stable, and the only meaningful difference 
    we can spot is caused by the less aggressive object mask in the very outskirt.

    We should also mention that we run \texttt{Ellipse} allowing for more 
    sophisticated shapes than a simple ellipse (4th Fourier modes that can make 
    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
    isophote better.
    We also apply the isophotes from $i$-band images to other bands in 
    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
    color profiles.  
%% ------------------------------------------------------------------------------------ %%

>>>>

    To derive reliable 1-D profile, it is important to mask out all the irrelevant 
    objects around the target.
    At the depth of the HSC images, this becomes a challenging task, especially 
    for massive galaxies with extended outer profiles and many satellites. 
    At this point, the \texttt{hscPipe} tends to over-subtract the background around 
    bright objects.  
    The performance of its deblending process is also not optimized for extended
    objects. 
    For these reasons, we perform \texttt{SExtractor}-like background subtraction and 
    object detection using the \texttt{SEP} Python library to generate the necessary 
    masks.
    Combining two different local background models and $S/N$ thresholds, we obtain 
    the centroid, shape, and radius that enclose 90\% of flux for each object, 
    including the one that is very close to the center of bright galaxy (left panel of 
    Fig~\ref{fig:ell_tech}). 
    Based on these information, we then create the mask that covers all contaminating 
    objects around the target after adaptively increasing the sizes of their masks 
    according to their brightness and distance to the central target. 
    Generally speaking, we mask out bright objects or objects in the outskirt of the 
    image more aggressively to reduce their impact on the surface brightness profiles 
    in the outskirt. 
    We also create masks that are less and more aggressive than the default one to 
    test their impacts on the surface brightness profiles.

    Next, we aggressively mask out all objects on the cut-out image.  
    We then evaluate the background level using the unmasked pixels after median 
    smoothing the masked image using box of $6x6$ pixels.
    This provides estimate of global background level along with its uncertainty. 
    Given the typical background uncertainty, the HSC \texttt{WIDE} image should be 
    able to reach down to $> 29$ \sb surface brightness level in the $i$-band.  
    However, as mentioned, we often find evidence of slightly over-subtracted 
    background for massive galaxies in our sample. 
    In the current \texttt{hscPipe}, the background on each CCD is modeled with a 
    Chebyshev-polynomial that is fit to the smoothed image after excluding pixels 
    with $S/N >5$.
    This algorithm performs much better than the SDSS version 
    (e.g.\ see \citealt{Blanton2011}), yet still over-subtracts background around 
    bright objects and results in unphysical truncation in their surface brightness 
    profiles.
    We empirically correct this issue using the background model generated by 
    the \texttt{SExtractor} algorithm on the masked image 
    ($200x200$ pixels background box size, and 6 pixels median filtering size of 
    sky boxes).
    This model can account for the slightly over-subtracted background at large scale,
    and reduce the impact from the low surface brightness ``wings'' of bright 
    neighbors. 
    We clearly see improvement in both the distributions of background pixels 
    (more symmetric distribution; median value is closer to 0) and the surface 
    brightness profile (middle panel of Fig~\ref{app:ellipse}; the negative intensity 
    and the turn-over of the curve-of-growth in the outskirt of the ``Original'' 
    profile are successfully corrected) after this correction.
    Also, it is worth mentioning that such correction does not often affect the 
    surface brightness profile within 100 kpc.

    The procedure used to derive 1-D surface brightness profile from the 
    background-corrected, contamination-masked images is already described in 
    Section~\ref{sec:ellipse} briefly. 
    In practice, the profile at very low surface brightness level is sensitive to 
    several \texttt{Ellipse} configurations.
    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    axis length between successive ellipses, and we use the median pixel value over the
    elliptical annulus after rejecting outlying pixels via $3\sigma$-clipping three
    times.
    We make the above choices to make the final profile less affected by any nearby
    object, and also test the differences between the profiles derived using larger
    step, or mean value on the annulus, or fewer times of $\sigma$-clipping. 
    Generally speaking, the surface brightness profile is very robust against these
    changes, especially within 100 kpc. 
    On the right panel of Fig~\ref{fig:ell_tech}, we compare the surface brightness
    profiles for an example massive galaxy using different masks and \texttt{Ellipse}
    parameters. 
    The profile within 100 kpc is very stable, and the only noticable difference 
    is caused by the less aggressive object-mask in the very outskirt.

    We should also mention that we run \texttt{Ellipse} allowing for more 
    sophisticated shapes than simple ellipse (4th Fourier modes that can make 
    isophote more ``disky'' or ``boxy'', e.g.\ \citealt{Kormendy2009}) to fit the 
    isophote better.
    We also apply the isophotes from $i$-band images to other bands in 
    ``force-photometry'' mode \texttt{Ellipse} run to get initial estimates of 
    color profiles.  
%% ------------------------------------------------------------------------------------ %%
